How the COVID-19 pandemic influenced the Death of Homeless people in Toronto? Drugs became the major reason

### 2024-01-24 outputs/paper/paper.qmd
toc change

---
title: "How the COVID-19 pandemic influenced the Death of Homeless people in Toronto? Drugs became the major reason"
subtitle: "Examining Trends in Age, Gender, and Causes of Death Among Toronto's Homeless Population from 2017 to 2023"
author: 
  - Yichen Ji
thanks: "Code and data are available at: https://github.com/Selinayichenji/2024-Data-collection.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
date-format: long
abstract: "By using 8 figures to analysis the data of homeless's death from 2017 to 2023, it was found that the major reason for increased death of homeless people during the Pandemic in Toronto was drug, instead of the COVID-19 itself. Only positioning the right problem enables us to take appropriate and efficient actions to help homeless people."
format: pdf
number-sections: true
bibliography: references.bib
#code referenced from posit community: https://community.rstudio.com/t/force-table-placement/149954
header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}

>>>>

---
title: "How the COVID-19 pandemic influenced the Death of Homeless people in Toronto? Drugs became the major reason"
subtitle: "Examining Trends in Age, Gender, and Causes of Death Among Toronto's Homeless Population from 2017 to 2023"
author: 
  - Yichen Ji
thanks: "Code and data are available at: https://github.com/Selinayichenji/2024-Data-collection.git."
date: "`r format(Sys.time(), '%d %B %Y')`"
date-format: long
abstract: "By using 8 figures to analysis the data of homeless's death from 2017 to 2023, it was found that the major reason for increased death of homeless people during the Pandemic in Toronto was drug, instead of the COVID-19 itself. Only positioning the right problem enables us to take appropriate and efficient actions to help homeless people."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
#code referenced from posit community: https://community.rstudio.com/t/force-table-placement/149954
header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
